
% 6. June

% Added ideas from Bill Pugh about how to integrate AI into programming.

4. March

\begin{itemize}
      \item Reworked sample course schedule
  \item Adding clarification to sampler to provide context in
    requirements table
  \item Added context to LEP and transfers / double majors
    \item Clarified that we will pursue an articulation agreement with
      at least one community college (and hopefully more)
    \item Added topics table to show connections between the courses
      \item Clarified relationship between 131 and 141 in LEP with an
        example
      \item Removed the different prefix for BA in AI courses
        \item Clarified that support for underrepresented groups
          begins with gateway courses
\end{itemize}

21. February

\begin{itemize}
  \item Reorganized core course figure
\end{itemize}

14. February

\begin{itemize}
    \item Friendly amendments from EdComm
\end{itemize}

11. February

\begin{itemize}
    \item Added proposed CS amendments to be voted on in CS Education Committee meeting.
    \item Minor clarification on computing infrastructure to make it understandable to non-CS folks.
\end{itemize}

6. February
\begin{itemize}
  \item Adding additional math courses that teach linear algebra
\end{itemize}

30. January, 2025
\begin{itemize}
  \item Amitabh Varshney identified logic error with enrollment assumptions in fifth year
  \item Adding additional electives after INFO shared new courses they are developing
  \item Removing electives that Linguistics no longer plans to offer 
  \item Adding additional descriptions
\end{itemize}

29. January, 2025
\begin{itemize}
  \item David Mount identified repeated courses
\end{itemize}

27. January, 2025
\begin{itemize}
    \item Adjusting prose from suggestions from Roger Eastman
    \item Administrative reporting adjustment
\end{itemize}

26. January, 2025
\begin{itemize}
  \item Additional FAQ questions, fixing errors pointed out by William Gasarch and Evan Golub.
\end{itemize}

20. January, 2025
\begin{itemize}
 \item Add accessibility specialization
 \item Addressing questions from Chris Kauffman
\end{itemize}

15. January, 2025
\begin{itemize}
\item Add AI Algorithms specialization
\end{itemize}

10. January, 2025
\begin{itemize}
  \item Sketch of Robotics and AI-powered communities concentrations
\end{itemize}

9. January, 2025

\begin{itemize}
  \item More clarity on where academic leadership lives
  \item Removing calculus requirement from AI 222
  
  \item Add prereqs to course descriptions
  \item Discussion of prereqs for out-of-major courses
\end{itemize}

6. January, 2025

\begin{itemize}
    \item Added text addressing GOFAI duplication
    \item Separated out those courses (per Chris Kauffman's suggestion) in the course listing
    \item Fixed some course numbers
\end{itemize}

7. January, 2025

\begin{itemize}
    \item Add sections required for the \abr{pcc} proposal including arguing for the \abr{lep}
    \item Fixed some clerical errors on requirements, typos in description
    \item Added section on recruiting a diverse student body
\end{itemize}

