\begin{enumerate}
\item \textbf{nan (CMSC 131)}: Introduction to programming and computer science. Emphasizes understanding and implementation of applications using object-oriented techniques. Develops skills such as program design and testing as well as implementation of programs using a graphical IDE. Programming done in Java.
\item \textbf{nan (CMSC 132)}: Introduction to use of computers to solve problems using software engineering principles. Design, build, test, and debug medium -size software systems and learn to use relevant tools. Use object-oriented methods to create effective and efficient problem solutions. Use and implement application programming interfaces (APIs). Programming done in Java.
\item \textbf{nan (INST 326)}: An introduction to programming, emphasizing understanding and
implementation of applications using object-oriented techniques. Topics to
be covered include program design and testing as well as implementation of
programs.
\item \textbf{nan (MATH 340)}: This is the first semester of the two-semester honors sequence Math 340-341 which gives a unified and enriched treatment of multivariable calculus, linear algebra, and ordinary differential equations, with supplementary material from differential geometry, Fourier series and calculus of variations.
\item \textbf{nan (MATH 140)}: Introduction to calculus, including functions, limits, continuity, derivatives and applications of the derivative, sketching of graphs of functions, introduction to definite and indefinite integrals, and calculation of area. The course is especially recommended for science and mathematics majors. Credit will be granted for only one of the following: MATH 140 or MATH 136 or MATH 120.
\item \textbf{nan (MATH 141)}Description TBD
\item \textbf{nan (CMSC 250)}Description TBD
\item \textbf{nan (MATH 250)}Description TBD
\item \textbf{nan (MATH 461)}: The course provides an introduction to linear algebra and matrix theory. It is intended primarily for engineering students. This course cannot be used toward the upper level math requirements for MATH/STAT majors. Credit will be granted for only one of the following: MATH 240, MATH 341, or MATH 461.
\item \textbf{nan (DATA 250)}:  Introduction to basic discrete mathematical and linear algebraic structures and use of these mathematical structures to solve programming problems. Logic, set theory, formal proof methodology, functions, and basic linear algebra.
\item \textbf{nan (MATH 240)}: Basic concepts of linear algebra: vector spaces, applications to line and plane geometry, linear equations and matrices, similar matrices, linear transformations, eigenvalues, determinants and quadratic forms. All sections of the course will use the software system MATLAB. Credit will be granted for only one of the following: MATH 240 or MATH 341 or MATH 461.
\item \textbf{nan (MATH 241)}: An introduction to multivariable calculus, including vectors and vector-valued functions, partial derivatives and applications of partial derivatives (such as tangent planes and Lagrange multipliers), multiple integrals, volume, surface area, and the classical theorems of Green, Stokes and Gauss. All sections of the course will use the software package MATLAB. Credit will be granted for only one of the following: MATH 241 or MATH 340.
\item \textbf{nan (MATH 341)}: This course is a continuation of MATH 340. The honors sequence MATH 340-341 covers roughly the same material of MATH 240, 241, and 246, but in greater depth and rigor. This semeseter will begin with remaining material from Multivariable Calculus (MATH 241) on extrema of functions of several variables and Lagrange multipliers. The remainder of the semester, and the bulk of the course, is then devoted to the theory of Ordinary Differential Equations (MATH 246).
\item \textbf{nan (INST 204)}: Reviews how specific values are built into different automated decision-making systems as an inevitable result of constructing mechanisms meant to produce specific outcomes. These values create differential outcomes for the different people enmeshed in these systems, but both these values and these systems can be changed to support different values and different outcomes. The class serves as an introduction to the emerging field of algorithmic bias that bridges the disciplines of information science, computer science, law, policy, philosophy, sociology, urban planning, and others.
\item \textbf{nan (LING 260)}: What is it about us humans and our languages that allows us to communicate in ways unmatched by other animals or powerful AI models? The question is ancient, but recent decades have seen great progress in the cognitive science of language, while expanding the diversity of languages investigated. We know much more about how languages vary, how they develop in children, how they are encoded in the mind, and relate to other domains of cognition. Major developments in statistical computation and research on animal cognition also illuminate what is (not) possible without the particular structure of the human mind. We bring this all to bear on our Big Question: What makes human language special from the viewpoint of meaning? Students will come to understand the major features of language as a vehicle for complex thought and a tool for communication. They will use this understanding in analyzing common semantic patterns and everyday conversational dynamics.
\item \textbf{nan (INST 414)}Description TBD
\item \textbf{nan (CMSC 320)}Description TBD
\item \textbf{nan (DATA 320)}Description TBD
\item \textbf{nan (CMSC 351)}Description TBD
\item \textbf{nan (CMSC 421)}: Introduces a range of ideas and methods in AI, varying semester to semester but chosen largely from: automated heuristic search, planning, games, knowledge representation, logical and statistical inference, learning, natural language processing, vision, robotics, cognitive modeling, and intelligent agents. Programming projects will help students obtain a hands-on feel for various topics.
\item \textbf{nan (CMSC 422)}: Machine Learning studies representations and algorithms that allow machines to improve their performance on a task from experience. This is a broad overview of existing methods for machine learning and an introduction to adaptive systems in general. Emphasis is given to practical aspects of machine learning and data mining.
\item \textbf{Introductory Linguistics (LING 200)}Description TBD
\item \textbf{Language and Mind (LING 240)}Description TBD
\item \textbf{Syntax I (LING 311)}Description TBD
\item \textbf{Grammar and Meaning (LING 410)}Description TBD
\item \textbf{Natural Language Processing (CMSC 470)}Description TBD
\item \textbf{Computer Vision (CMSC 426)}Description TBD
\item \textbf{Computer Graphics (CMSC 427)}Description TBD
\item \textbf{Phonetics (LING 320)}Description TBD
\item \textbf{Phonology I (LING 321)}Description TBD
\item \textbf{Phonology II (LING 322)}Description TBD
\item \textbf{Historical Linguistics (LING 330)}Description TBD
\end{enumerate}